\section{Problem Definition}
\label{sec:1_introduction_problem}
In the rapidly evolving landscape of machine learning, the surge in high-speed data streams has brought forth a formidable challenge — effectively managing non-stationary data environments. This challenge is characterized by dynamic shifts in statistical properties, underlying concepts, and data distributions over time. The fundamental obstacle arises when models, initially trained on historical data, encounter diminishing accuracy when confronted with new data affected by concept drift.

In this dynamic context, the specific challenges include the emergence class problem, characterized by the unforeseen appearance of classes do not present during the model's initial training, particularly in real-time streaming scenarios. Additionally, challenges encompass imbalanced multi-class streams and heterogeneous transfer learning. These issues intricately complicate the task of maintaining accurate and up-to-date models, as traditional learning approaches are inadequately equipped to cope with the spontaneity introduced by the sudden emergence of classes or the shifting in data distribution. Key facets of this intricate problem include:
\begin{itemize}
    \item \textbf{Concept Drift Management}: Non-stationary data streams inherently exhibit concept drift, demanding effective detection and response mechanisms to the changing landscape of underlying concepts, relationships, or data distributions.
    \item \textbf{Optimization of Classifier Ensembles}: Frameworks need to be developed that can dynamically optimize classifier ensembles based on evolving data characteristics. This optimization is crucial for enhancing accuracy and effectiveness, especially when dealing with emergent classes.
    \item \textbf{Real-Time Adaptation}: Given the dynamic nature of non-stationary data streams, frameworks must facilitate real-time adaptation and refinement of classification models to seamlessly navigate the ever-changing data landscapes.
    \item \textbf{Emerging New Classes}: The challenge is to devise models that can dynamically adapt to the sudden appearance of new classes in real-time streaming data, ensuring a seamless integration without compromising overall accuracy.
    \item \textbf{Multi-Class Imbalance Non-stationary Streams}: The presence of imbalanced data distributions within multi-class scenarios complicates the landscape. Robust strategies are required to address class imbalances and optimize classifier performance.
    \item \textbf{Heterogenous Transfer Learning in Dynamic Environments}: The transfer of knowledge from diverse source domains to the target domain becomes pivotal for sustaining model performance. Techniques that bridge domain gaps and mitigate negative knowledge transfer are essential.
\end{itemize}
